Naturalness in U(1) extensions of the MSSM

### 2014-12-18 paper/e6ssm-tuning-paper.tex
Added complete list of fixed parameters for first set of plots, if they are needed, and fixed broken figure reference

% DH:: I'm not sure if this is worth including? I've put a disclaimer in the
% text, as well.
\begin{figure}[h]
\begin{center}
\resizebox{!}{10cm}{%
\includegraphics{mssm_higgs_tuning.png}}
\caption{Scatter plot of fine tuning in the MSSM as a function of
the lightest Higgs mass, $m_{h_1}$, for the cut-off scales (from 
bottom to top) $M_X=20$ TeV, $M_X=50$ TeV, $M_X=100$ TeV and $M_X=10^{16}$ GeV.}
\label{Fig:mssmhiggstuning}
\end{center}
\end{figure}
To illustrate this, in Fig.~\ref{Fig:mssmstoptuning} we show the variation in fine
tuning when we fix $\mu=-97$ GeV and $B=-85$ GeV, and scan over the
stop masses and mixing, with $500 \textrm{ GeV} \leq
m_{Q_3},m_{u_3}\leq 10\textrm{ TeV}$ and $-3810\textrm{ GeV}\leq
A_t\leq -20\textrm{ GeV}$, for $M_X=20$ TeV, $50$ TeV and $100$ TeV.
Note that the Higgs mass is also allowed to vary over the scan, as shown in 
Fig.~\ref{Fig:mssmhiggstuning}.
However this tuning only really becomes large for very large stop
masses.  On the other hand if the cuttoff is increased then stop masses of
several TeV can result in tuning of [insert] as shown in
Fig.~\ref{Fig:mssmstopstuning}.\\ \\

>>>>

% DH:: I'm not sure if this is worth including? I've put a disclaimer in the
% text, as well.
\begin{figure}[h]
\begin{center}
\resizebox{!}{10cm}{%
\includegraphics{mssm_higgs_tuning.png}}
\caption{Scatter plot of fine tuning in the MSSM as a function of
the lightest Higgs mass, $m_{h_1}$, for the cut-off scales (from 
bottom to top) $M_X=20$ TeV, $M_X=50$ TeV, $M_X=100$ TeV and $M_X=10^{16}$ GeV.}
\label{Fig:mssmhiggstuning}
\end{center}
\end{figure}
To illustrate this, in Fig.~\ref{Fig:mssmstoptuning} we show the variation in fine
tuning when we scan over the
stop masses and mixing, with $500 \textrm{ GeV} \leq
m_{Q_3},m_{u_3}\leq 10\textrm{ TeV}$ and $-3810\textrm{ GeV}\leq
A_t\leq -20\textrm{ GeV}$, for $M_X=20$ TeV, $50$ TeV and $100$ TeV.
The remaining parameters we fix such that at $M_{SUSY}$ they have the values $\mu=-97.5$ GeV, $B=-84.8$ GeV,
$M_1=92.1$ GeV, $M_2=95.9$ GeV, $M_3=352$ GeV, $A_b=-117.9$ GeV, $A_\tau=-7.8$ GeV, $m_{L_i}=400$ GeV, $m_{e_i}=204$ GeV,
$m_{Q_{1,2}}=438$ GeV, $m_{u_{1,2}}436$ GeV and $m_{d_i}=438$ GeV ($i=1,2,3$). 
Note that the Higgs mass is also allowed to vary over the scan, as shown in 
Fig.~\ref{Fig:mssmhiggstuning}.
However this tuning only really becomes large for very large stop
masses.  On the other hand if the cuttoff is increased then stop masses of
several TeV can result in tuning of [insert] as shown in
Fig.~\ref{Fig:mssmstoptuning}.\\ \\
